\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
Results restructuring

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split. We only evaluated the best performing model (with respect to
\textit{AUROC} and $MicroAUC_p$) on the Yamanishi benchmark dataset.

>>>>

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC} and $MicroAUC_p$) and evaluate them on the Yamanishi
benchmark dataset.
